### 2024-07-25 paper.tex
finish other sl2-triple

\subsection{Finding an \(\spl_2\)-triple in a slightly less simple case}
Now, let 
\[E = \begin{pmatrix}
    0 & 0 \\
    0 & e
\end{pmatrix} \in \spl_{m + n},\]
with \(e\) as in the previous subsection.
We will find \(H, F\) so that \((E, H, F)\) is an \(\spl_2\)-triple.
Writing \(F = \begin{pmatrix}
    F_{11} & F_{12} \\
    F_{21} & f
\end{pmatrix}\), and similarly for \(H\), we have
\[2E = [H, E] = \begin{pmatrix}
    0 & H_{12}e \\
    0 & he
\end{pmatrix} - \begin{pmatrix}
    0 & 0 \\
    e H_{21} & eh
\end{pmatrix},\]
\[H = [E, F] = \begin{pmatrix}
    0 & 0 \\
    e F_{21} & ef
\end{pmatrix} - \begin{pmatrix}
    0 & F_{12}e \\
    0 & fe
\end{pmatrix}.\]
From these we observe that \((e, h, f)\) must also be an \(\spl_2\)-triple, so \(h, f\) must be as in the previous subsection.
We also see that \(H_{11} = 0\).
Recalling that left multiplication by \(e\) is a down-shift, and right multiplication is a left-shift, we see that \(H_{12}\) is all zeroes except for the leftmost column, and \(H_{21}\) is all zeroes except for the bottom row.
Similarly for \(F_{12}\) and \(F_{21}\).
Then our final constraint is that 
\[-2F = [H, F] = \]
\[\begin{pmatrix}
    H_{12} F_{21} & H_{12} F_{22} \\
    H_{21} F_{11} + H_{22} F_{21} & H_{21} F_{12} + H_{22} F_{22}
\end{pmatrix} - \begin{pmatrix}
    F_{12} H_{21} & F_{11} H_{12} + F_{12} H_{22} \\
    F_{22} H_{21} & F_{21} H_{12} + F_{22} H_{22}
\end{pmatrix}.\]
Now \(H_{12} F_{21} = F_{12} H_{21} = 0\), by our facts about them from further above.
By the equation above then, we also get \(F_{11} = 0\).
So, the equation above simplifies to 
\[-2F = \begin{pmatrix}
    0 & H_{12} f \\
    h F_{21} & H_{21} F_{12}
\end{pmatrix} - \begin{pmatrix}
    0 & F_{12} h \\
    f H_{21} & F_{21} H_{12}
\end{pmatrix}.\]

>>>>

\subsection{Finding an \(\spl_2\)-triple in a slightly less simple case}
Now, let 
\[E = \begin{pmatrix}
    0 & 0 \\
    0 & e
\end{pmatrix} \in \spl_{m + n},\]
with \(e\) as in the previous subsection.
We will find \(H, F\) so that \((E, H, F)\) is an \(\spl_2\)-triple.
Writing \(F = \begin{pmatrix}
    F_{11} & F_{12} \\
    F_{21} & f
\end{pmatrix}\), and similarly for \(H\), we have
\[2E = [H, E] = \begin{pmatrix}
    0 & H_{12}e \\
    0 & he
\end{pmatrix} - \begin{pmatrix}
    0 & 0 \\
    e H_{21} & eh
\end{pmatrix},\]
\[H = [E, F] = \begin{pmatrix}
    0 & 0 \\
    e F_{21} & ef
\end{pmatrix} - \begin{pmatrix}
    0 & F_{12}e \\
    0 & fe
\end{pmatrix}.\]
From these we observe that \((e, h, f)\) must also be an \(\spl_2\)-triple, so \(h, f\) must be as in the previous subsection.
We also see that \(H_{11} = 0\).
Recalling that left multiplication by \(e\) is a down-shift, and right multiplication is a left-shift, we see that \(H_{12}\) is all zeroes except for the leftmost column, and \(H_{21}\) is all zeroes except for the bottom row.
% Then \(F_{12}\) must be all zeros except for the two leftmost columns, and \(F_{21}\) must be all zeroes except for the bottom two rows.
Then our final constraint is that 
\[-2F = [H, F] = \]
\[\begin{pmatrix}
    H_{12} F_{21} & H_{12} F_{22} \\
    H_{21} F_{11} + H_{22} F_{21} & H_{21} F_{12} + H_{22} F_{22}
\end{pmatrix} - \begin{pmatrix}
    F_{12} H_{21} & F_{11} H_{12} + F_{12} H_{22} \\
    F_{22} H_{21} & F_{21} H_{12} + F_{22} H_{22}
\end{pmatrix}.\]
Now \(H_{12} = F_{12}e\), and \(H_{21} = eF_{21}\), from the equation \(H = [E, F]\).
Substituting in the equation above then,
\[-2F = \begin{pmatrix}
    F_{12} e F_{21} & F_{12}e f \\
    eF_{21} F_{11} + h F_{21} & eF_{21} F_{12} + hf
\end{pmatrix} - \begin{pmatrix}
    F_{12} e F_{21} & F_{11} F_{12}e + F_{12} h \\
    f eF_{21} & F_{21} F_{12}e + fh
\end{pmatrix} =\]
\[\begin{pmatrix}
    0 & F_{12}(fe + h) \\
    eF_{21} F_{11} + h F_{21} & eF_{21} F_{12} + hf
\end{pmatrix} - \begin{pmatrix}
    0 & F_{11} F_{12}e + F_{12} h \\
    (ef - h)F_{21} & F_{21} F_{12}e + fh
\end{pmatrix} =\]
\[\begin{pmatrix}
    0 & F_{12}fe \\
    eF_{21} F_{11} & eF_{21} F_{12} + hf
\end{pmatrix} - \begin{pmatrix}
    0 & F_{11} F_{12}e \\
    ef F_{21} & F_{21} F_{12}e + fh
\end{pmatrix}.\]
Now we see that \(F_{11} = 0\), and consequently that \(F_{12} = F_{21} = 0\) as well.
This shows that \(H_{12} = H_{21} = 0\).
We conclude that \(H\) and \(F\) just have \(h\) and \(f\) in their bottom-right corners, respectively.
